### 2025-08-26 Scripts/Manuscript/manuscript.Rmd
fixed minor errors in the Rmarkdown text.

---
title             : "Assessing Reliable and Valid Measurement as a Prerequisite for Informative Replications in Psychology"
shorttitle        : "Measurement and Informative Replications"

@@

The challenge with measurement in quantitative psychological research is that psychological constructs cannot be directly measured like height or weight. Instead, we use scores from a measurement as a proxy indicator for that psychological construct. However, we cannot simply assume that any measure we create will form a good indicator of the construct. We have to substantiate this. Psychometrics can be used to statistically estimate properties of the measure that are indicative of its validity. The effort of validating a measure represents a research effort all on its own. Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher using a measure as part of their broader aim to study a psychological phenomena. When the effort involved in validating a measure is relegated to being only a component of a study that is more focused on the testing of a phenomena, we have to wonder, how well does this measurement validation process go?

## Measurement Validation

When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022]. Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest [@crutzenScaleQualityAlpha2017b]. Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores. The number of factors are first specified, and then the fit of a model involving those number of factors is determined. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate. However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary. Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951]. Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself. In spite of this many researchers report and interpret Cronbach's Alpha as such [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].

Thus, psychometric tests are useful but they are not always easy to perform in practice. Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999). However, even in the latter case factor analysis does not converge with low sample sizes. Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with generally even larger sample sizes per group to detect meaningful effects [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018]. However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. Finally, @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data, the results. They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.

@@

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020]. @flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. But reporting of reliability and validity evidence is not only low, but may also be biased as well. @husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (!!!exact numbers!!!). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several aspects of the measurement reporting practices in replications and original articles. Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs. Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together. This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study. Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research. While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere [@gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].

@@

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs of a Many Labs replication. For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data\$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data\$g)), 0)` lab locations for our analyses.

@@

After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here. A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd). The items are currently used as individual descriptives on the reporting practices in our sample.

@@

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a to calculate the standard error in the meta-analysis. Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998]. Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954]. These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010]. Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye [@borensteinAvoidingCommonMistakes2024]. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

Finally, we also tested these measures for unidimensionality. Our unidimensionality check serves a double purpose. First, unidimensionality is one of the assumptions of Cronbach's Alpha. If this assumption does not hold for a measure, Cronbach's Alpha gives a biased and uninformative estimate of the reliability. Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent vasriable. Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence). Still, we believe it is not unreasonable to assume that for most of our measures we should observe a unidimensional factor model to have at least adequate fit.

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.

@@

```{r validity_evidence_reporting}
table(coded_data_original$sel_psychometric_evidence_REV)
table(coded_data_replications$sel_psychometric_evidence_REV)

@@

```{r PlotData1FactorRMSEA}
unidimensionality_graph_data <- data.frame(RMSEA = c(NA),
                                           RMSEA_se = c(NA),
                                           N_factors = NA,
                                           unidimensional = NA,
                                           g = NA)

@@

for (i in 1:19){

@@

```{r Plot1Factor, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted. The red horizontal line separate the replicated from the non-repicated measures. The red vertical line indicates our .08 RMSEA cutoff value. The N non-conv. column besides the graph shows the number of labs per measure for which the single-factor CFA did not converge. The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses. Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies."}

@@

```{r check_on_Omega_convergence}
is_mostly_na <- function(x){
  return((sum(is.na(x)) / length(x)) > .5) 
}

@@

sum(Omega_convergence_vector)
```

@@

```{r PlotOmegaDistributions, warning = false, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated. The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated. Due to lack of underlying model convergence an Omega coefficient could not be calculated for all lab locations, or any lab locations for the Der Fruyt et al. (2000) measure. The N.tot column shows the total number of lab locations at which the measure was taken. Any difference between N.omg and N.tot can be seen as an indication of the instability to get a stable estimate of an underlying facto model for some lab locations for that measure."}
# plot for omega
ggplot(calculated_alpha_plot_data, aes(x = omega.tot, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(alpha = 0.1) +

@@

```{r QMPtable}
# create informative Measurement Practice Labels 
MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",   "The measured variable is defined", "The choice of measure selection or creation is justified",    "The implemented operationalisation is justified", "The source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "The administration format and environment are described", "The administration procedure is described",   "The number of items are described", "The number of response options are described",    "The recoding of responses is described", "The creation of the index is described",    "Example items are presented in text or supplement", "Any administration format changes are mentioned",    "Administration format changes are justified/validated", "Any translations are mentioned",    "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned",    "Changes in number of items or response options are justified/validated")

>>>>

---
title             : "Measurement Reliabily, Validity, and Reporting in Replicaitons and Original Research"
shorttitle        : "Measurement Reliability, Validity, and Reporting"

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured. Instead we use scores from a measurement as a proxy indicator for that psychological construct. However, we cannot simply assume that any measure we create will form a good indicator of the construct. We have to substantiate this. Psychometrics can be used to statistically estimate the measure's validity, still validating a measure entails a substantial research effort. Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher conducting a study of a psychological phenomenon. When the effort involved in validating a measure is relegated to be only a component of a study, then how well does the measurement validation process go?

## Measurement Validation
When validating a measure of a psychological construct, two main psychometric components are of interest: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in unobserved constructs between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022]. Reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. Reliability is part of the validation of a measure because a measure that does not consistently capture a participant's response, cannot accurately capture a construct [@crutzenScaleQualityAlpha2017b]. As an example, suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, or weighted averages of the item scores. To fit a factor model, the number of factors are first specified, and then the fit of that model on the data can be evaluated. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit on the data. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model on our intelligence measure to show adequate fit, with one factor to which only items 1 through 5 relate strongly, and one to which only items 6 through 10 relate strongly. However, even in this ideal scenario, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability for single measurement instances is through internal consistency indicators. The most common internal consistency indicator is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951]. Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability within a particular sample and not of the reliability of the measure in general. Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].

Thus, psychometric tests are useful but they have their limitations. Even simple factor analyses - unless the amount of variance explained by the factors is large and the factor structure is clear - require sample sizes of at least 100 [@maccallumSampleSizeFactor1999; @gorsuchFactorAnalysis2013]. Furthermore, even in the latter case factor analysis may not converge with small sample sizes. If we want to know the reliability and validity of not just one measurement but for the measure across multiple contexts, we need to conduct multiple studies. Additionally, larger sample sizes per relevant group to detect meaningful effects when checking for measurement invariance across groups [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018]. However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025], let alone that they are systematically tested on reliability and validity. @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data. They observed that for the scales they assessed, no factor model fit congruent with the use of the scales met all of their evaluation criteria. Furthermore, the overall sample Cronbach's alpha level of all scales was below .5, a level of reliability far below what many would consider acceptable for almost all research purposes.

@@

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020]. @flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. Furthermore, reporting of reliability may not only be little, but also biased. @husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of that measurement. The lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular (!!!exact numbers!!!). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially different way, or even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. On the other hand, if the same constructs are assessed very differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several measurement reporting practices in replications and original articles. Additionally, we estimated reliability and validity from openly available replication data on item responses. This replication data was available across multiple labs. Our unique contribution is based on the combination of reported and the recalculated measurement information. These two sources combined allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement and validate it in a new study. Besides this, our study also functions as a conceptual replication of existing research on reporting practices and measurement validation, by assessing measurement reporting differently and using a novel set of replications and original research. While theoretical considerations are  key for evaluating how the content of the measure fits to the constructs of interest, we do not look into these here. Evaluating the theory of a measurement requires domain specific knowledge for each measure which is outside of this article's scope. We refer interested readers to articles discussing theory in measurement elsewhere [e.g.; @gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].

@@

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@kleinManyLabs42022] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs of each Many Labs replication. For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.

@@

After the initial coding, we made minor revisions to fourteen of the twenty QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here in the main article. A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).

@@

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a. Then we entered these two values into a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998]. Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954]. These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010]. Therefore, we also present the prediction interval and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024]. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because it is common in research, which also allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

Finally, we also tested these measures for unidimensionality. Our unidimensionality check serves a double purpose. First, unidimensionality is one of the assumptions of Cronbach's Alpha. If this assumption does not hold for a measure, our Cronbach's Alpha estimates give a biased estimate of the reliability. Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent variable. Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence). Still, we believe it is not unreasonable to assume that for most of the single index measures we should observe a unidimensional factor model to have at least adequate fit.

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.

@@

```{r validity_evidence_reporting, include = FALSE, eval = FALSE}
table(coded_data_original$sel_psychometric_evidence_REV)
table(coded_data_replications$sel_psychometric_evidence_REV)

@@

```{r PlotData1FactorRMSEA, warning = FALSE}
# load in the FA_list data
FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
                fa_shnabel_2008, fa_vohs_2008)

# create the base dataframe
unidimensionality_graph_data <- data.frame(RMSEA = c(NA),
                                           RMSEA_se = c(NA),
                                           N_factors = NA,
                                           unidimensional = NA,
                                           g = NA)

@@

# adding the info from the FA_list to our data.
for (i in 1:19){

@@

```{r Plot1Factor, warning = FALSE, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted. The red horizontal line separate the replicated from the non-repicated measures. The red vertical line indicates our .08 RMSEA cutoff value. The N non-conv. column besides the graph shows the number of labs per measure for which the single-factor CFA did not converge. The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses. Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies."}

@@

```{r check_on_Omega_convergence, warning = FALSE}
is_mostly_na <- function(x){
  return((sum(is.na(x)) / length(x)) > .5) 
}

@@

# sum(Omega_convergence_vector)
```

@@

```{r PlotOmegaDistributions, warning = FALSE, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated. The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated. Due to lack of underlying model convergence an Omega coefficient could not be calculated for all lab locations, or any lab locations for the Der Fruyt et al. (2000) measure. The N.tot column shows the total number of lab locations at which the measure was taken. Any difference between N.omg and N.tot can be seen as an indication of the instability to get a stable estimate of an underlying facto model for some lab locations for that measure."}
# plot for omega
ggplot(calculated_alpha_plot_data, aes(x = omega.tot, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(alpha = 0.1) +

@@

```{r QMPTable}
# create informative Measurement Practice Labels 
MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
